
Check stats for brms models
Chaofei 2023.5.13

```{r include=F}
#source('figure_perturbation.R')
library(brms)
load('brms_fit.RData')
```

# Bi opto
## test for bi opto delta raw_rho
```{r echo=T, comment=NA}

hyp_opto_rho <- hypothesis(bi_opto_cdf, "exp(logrho_Intercept + logrho_dose) - exp(logrho_Intercept) < 0", alpha = 0.025)
hyp_opto_rho
plot(hyp_opto_rho)
```

## bi opto logrho_dose
```{r echo=T, comment=NA}

hyp_opto_rho_dose <- hypothesis(bi_opto_cdf, "logrho_dose < 0", alpha = 0.025)
hyp_opto_rho_dose
plot(hyp_opto_rho_dose)
```


## test for bi opto delta raw noise
```{r echo=T, comment=NA}

hyp_opto_noise <- hypothesis(bi_opto_cdf, "exp(noise_Intercept + noise_dose) - exp(noise_Intercept) > 0", alpha = 0.025)
hyp_opto_noise
plot(hyp_opto_noise)
```


## bi opto lognoise_dose
```{r echo=T, comment=NA}

hyp_opto_noise_dose <- hypothesis(bi_opto_cdf, "noise_dose > 0", alpha = 0.025)
hyp_opto_noise_dose
plot(hyp_opto_noise_dose)
```


## test for bi opto delta omega rational
```{r echo=T, comment=NA}

hyp_opto_omega_rational <- hypothesis(bi_opto_cdf, "inv_logit(omega1_Intercept + omega1_dose) - inv_logit(omega1_Intercept) < 0", alpha = 0.025)
hyp_opto_omega_rational
plot(hyp_opto_omega_rational)
```

## bi opto omega1_dose
```{r echo=T, comment=NA}

hyp_opto_omega1_dose <- hypothesis(bi_opto_cdf, "omega1_dose < 0", alpha = 0.025)
hyp_opto_omega1_dose
plot(hyp_opto_omega1_dose)
```


## test for bi opto delta omega lottery
```{r echo=T, comment=NA}

hyp_opto_omega_lottery <- hypothesis(bi_opto_cdf, "(1- inv_logit(omega1_Intercept + omega1_dose))*inv_logit(omega2_Intercept + omega2_dose) - (1- inv_logit(omega1_Intercept))*inv_logit(omega2_Intercept) < 0", alpha = 0.025)
hyp_opto_omega_lottery
plot(hyp_opto_omega_lottery)
```


## bi opto omega2_dose
```{r echo=T, comment=NA}

hyp_opto_omega2_dose <- hypothesis(bi_opto_cdf, "omega2_dose < 0", alpha = 0.025)
hyp_opto_omega2_dose
plot(hyp_opto_omega2_dose)
```

## test for bi opto delta omega surebet
```{r echo=T, comment=NA}

hyp_opto_omega_surebet <- hypothesis(bi_opto_cdf, "(1- inv_logit(omega1_Intercept + omega1_dose))*(1-inv_logit(omega2_Intercept + omega2_dose)) - (1- inv_logit(omega1_Intercept))*(1-inv_logit(omega2_Intercept)) > 0", alpha = 0.025)
hyp_opto_omega_surebet
plot(hyp_opto_omega_surebet)
```

# unilateral opto
## test for uni opto delta raw_rho
```{r echo=T, comment=NA}

hyp_opto_rho <- hypothesis(uni_opto_cdf, "exp(logrho_Intercept + logrho_dose) - exp(logrho_Intercept) < 0", alpha = 0.025)
hyp_opto_rho
plot(hyp_opto_rho)
```

## uni opto logrho_dose
```{r echo=T, comment=NA}

hyp_opto_rho_dose <- hypothesis(uni_opto_cdf, "logrho_dose < 0", alpha = 0.025)
hyp_opto_rho_dose
plot(hyp_opto_rho_dose)
```


## test for uni opto delta raw noise
```{r echo=T, comment=NA}

hyp_opto_noise <- hypothesis(uni_opto_cdf, "exp(noise_Intercept + noise_dose) - exp(noise_Intercept) > 0", alpha = 0.025)
hyp_opto_noise
plot(hyp_opto_noise)
```


## uni opto lognoise_dose
```{r echo=T, comment=NA}

hyp_opto_noise_dose <- hypothesis(uni_opto_cdf, "noise_dose > 0", alpha = 0.025)
hyp_opto_noise_dose
plot(hyp_opto_noise_dose)
```


## test for uni opto delta omega rational
```{r echo=T, comment=NA}

hyp_opto_omega_rational <- hypothesis(uni_opto_cdf, "inv_logit(omega1_Intercept + omega1_dose) - inv_logit(omega1_Intercept) < 0", alpha = 0.025)
hyp_opto_omega_rational
plot(hyp_opto_omega_rational)
```

## uni opto omega1_dose
```{r echo=T, comment=NA}

hyp_opto_omega1_dose <- hypothesis(uni_opto_cdf, "omega1_dose < 0", alpha = 0.025)
hyp_opto_omega1_dose
plot(hyp_opto_omega1_dose)
```


## test for uni opto delta omega lottery
```{r echo=T, comment=NA}

hyp_opto_omega_lottery <- hypothesis(uni_opto_cdf, "(1- inv_logit(omega1_Intercept + omega1_dose))*inv_logit(omega2_Intercept + omega2_dose) - (1- inv_logit(omega1_Intercept))*inv_logit(omega2_Intercept) < 0", alpha = 0.025)
hyp_opto_omega_lottery
plot(hyp_opto_omega_lottery)
```


## uni opto omega2_dose
```{r echo=T, comment=NA}

hyp_opto_omega2_dose <- hypothesis(uni_opto_cdf, "omega2_dose < 0", alpha = 0.025)
hyp_opto_omega2_dose
plot(hyp_opto_omega2_dose)
```

## test for uni opto delta omega surebet
```{r echo=T, comment=NA}

hyp_opto_omega_surebet <- hypothesis(uni_opto_cdf, "(1- inv_logit(omega1_Intercept + omega1_dose))*(1-inv_logit(omega2_Intercept + omega2_dose)) - (1- inv_logit(omega1_Intercept))*(1-inv_logit(omega2_Intercept)) > 0", alpha = 0.025)
hyp_opto_omega_surebet
plot(hyp_opto_omega_surebet)
```

# bilateral fof muscimol
## test for bi muscimol delta raw rho
```{r echo=T, comment=NA}

hyp_muscimol_rho <- hypothesis(bi_fof_muscimol_cdf, "exp(logrho_Intercept + logrho_dose) - exp(logrho_Intercept) < 0", alpha = 0.025)
hyp_muscimol_rho
plot(hyp_muscimol_rho)
```

## bi muscimol logrho_dose
```{r echo=T, comment=NA}

hyp_muscimol_rho_dose <- hypothesis(bi_fof_muscimol_cdf, "logrho_dose < 0", alpha = 0.025)
hyp_muscimol_rho_dose
plot(hyp_muscimol_rho_dose)
```


## test for bi muscimol delta raw noise
```{r echo=T, comment=NA}

hyp_muscimol_noise <- hypothesis(bi_fof_muscimol_cdf, "exp(noise_Intercept + noise_dose) - exp(noise_Intercept) > 0", alpha = 0.025)
hyp_muscimol_noise
plot(hyp_muscimol_noise)
```

## bi muscimol lognoise_dose
```{r echo=T, comment=NA}

hyp_muscimol_noise_dose <- hypothesis(bi_fof_muscimol_cdf, "noise_dose > 0", alpha = 0.025)
hyp_muscimol_noise_dose
plot(hyp_muscimol_noise_dose)
```


## test for bi muscimol delta rational
```{r echo=T, comment=NA}

hyp_muscimol_omega_rational <- hypothesis(bi_fof_muscimol_cdf, "inv_logit(omega1_Intercept + omega1_dose) - inv_logit(omega1_Intercept) < 0", alpha = 0.025)
hyp_muscimol_omega_rational
plot(hyp_muscimol_omega_rational)
```

## bi muscimol omega1_dose
```{r echo=T, comment=NA}

hyp_muscimol_omega1_dose <- hypothesis(bi_fof_muscimol_cdf, "omega1_dose < 0", alpha = 0.025)
hyp_muscimol_omega1_dose
plot(hyp_muscimol_omega1_dose)
```


## test for bi muscimol delta lottery
```{r echo=T, comment=NA}

hyp_muscimol_omega_lottery <- hypothesis(bi_fof_muscimol_cdf, "(1- inv_logit(omega1_Intercept + omega1_dose))*inv_logit(omega2_Intercept + omega2_dose) - (1- inv_logit(omega1_Intercept))*inv_logit(omega2_Intercept) < 0", alpha = 0.025)
hyp_muscimol_omega_lottery
plot(hyp_muscimol_omega_lottery)
```


## bi muscimol omega2_dose
```{r echo=T, comment=NA}

hyp_muscimol_omega2_dose <- hypothesis(bi_fof_muscimol_cdf, "omega2_dose < 0", alpha = 0.025)
hyp_muscimol_omega2_dose
plot(hyp_muscimol_omega2_dose)
```

## test for bi muscimol delta surebet
```{r echo=T, comment=NA}

hyp_muscimol_omega_surebet <- hypothesis(bi_fof_muscimol_cdf, "(1- inv_logit(omega1_Intercept + omega1_dose))*(1-inv_logit(omega2_Intercept + omega2_dose)) - (1- inv_logit(omega1_Intercept))*(1-inv_logit(omega2_Intercept)) > 0", alpha = 0.025)
hyp_muscimol_omega_surebet
plot(hyp_muscimol_omega_surebet)
```

# unilateral fof muscimol
## test for uni muscimol delta raw rho
```{r echo=T, comment=NA}

hyp_muscimol_rho <- hypothesis(uni_fof_muscimol_cdf, "exp(logrho_Intercept + logrho_dose) - exp(logrho_Intercept) < 0", alpha = 0.025)
hyp_muscimol_rho
plot(hyp_muscimol_rho)
```

## uni muscimol logrho_dose
```{r echo=T, comment=NA}

hyp_muscimol_rho_dose <- hypothesis(uni_fof_muscimol_cdf, "logrho_dose < 0", alpha = 0.025)
hyp_muscimol_rho_dose
plot(hyp_muscimol_rho_dose)
```


## test for uni muscimol delta raw noise
```{r echo=T, comment=NA}

hyp_muscimol_noise <- hypothesis(uni_fof_muscimol_cdf, "exp(noise_Intercept + noise_dose) - exp(noise_Intercept) > 0", alpha = 0.025)
hyp_muscimol_noise
plot(hyp_muscimol_noise)
```

## uni muscimol lognoise_dose
```{r echo=T, comment=NA}

hyp_muscimol_noise_dose <- hypothesis(uni_fof_muscimol_cdf, "noise_dose > 0", alpha = 0.025)
hyp_muscimol_noise_dose
plot(hyp_muscimol_noise_dose)
```


## test for uni muscimol delta rational
```{r echo=T, comment=NA}

hyp_muscimol_omega_rational <- hypothesis(uni_fof_muscimol_cdf, "inv_logit(omega1_Intercept + omega1_dose) - inv_logit(omega1_Intercept) < 0", alpha = 0.025)
hyp_muscimol_omega_rational
plot(hyp_muscimol_omega_rational)
```

## uni muscimol omega1_dose
```{r echo=T, comment=NA}

hyp_muscimol_omega1_dose <- hypothesis(uni_fof_muscimol_cdf, "omega1_dose < 0", alpha = 0.025)
hyp_muscimol_omega1_dose
plot(hyp_muscimol_omega1_dose)
```


## test for uni muscimol delta lottery
```{r echo=T, comment=NA}

hyp_muscimol_omega_lottery <- hypothesis(uni_fof_muscimol_cdf, "(1- inv_logit(omega1_Intercept + omega1_dose))*inv_logit(omega2_Intercept + omega2_dose) - (1- inv_logit(omega1_Intercept))*inv_logit(omega2_Intercept) < 0", alpha = 0.025)
hyp_muscimol_omega_lottery
plot(hyp_muscimol_omega_lottery)
```


## uni muscimol omega2_dose
```{r echo=T, comment=NA}

hyp_muscimol_omega2_dose <- hypothesis(uni_fof_muscimol_cdf, "omega2_dose < 0", alpha = 0.025)
hyp_muscimol_omega2_dose
plot(hyp_muscimol_omega2_dose)
```

## test for uni muscimol delta surebet
```{r echo=T, comment=NA}

hyp_muscimol_omega_surebet <- hypothesis(uni_fof_muscimol_cdf, "(1- inv_logit(omega1_Intercept + omega1_dose))*(1-inv_logit(omega2_Intercept + omega2_dose)) - (1- inv_logit(omega1_Intercept))*(1-inv_logit(omega2_Intercept)) > 0", alpha = 0.025)
hyp_muscimol_omega_surebet
plot(hyp_muscimol_omega_surebet)
```


# check the ppc data

## test for bi muscimol delta raw rho
```{r echo=T, comment=NA}

hyp_muscimol_rho <- hypothesis(bi_ppc_muscimol_cdf_40, "exp(logrho_Intercept + logrho_dose) - exp(logrho_Intercept) < 0", alpha = 0.025)
hyp_muscimol_rho
plot(hyp_muscimol_rho)
```

## bi muscimol logrho_dose
```{r echo=T, comment=NA}

hyp_muscimol_rho_dose <- hypothesis(bi_ppc_muscimol_cdf_40, "logrho_dose < 0", alpha = 0.025)
hyp_muscimol_rho_dose
plot(hyp_muscimol_rho_dose)
```


## test for bi muscimol delta raw noise
```{r echo=T, comment=NA}

hyp_muscimol_noise <- hypothesis(bi_ppc_muscimol_cdf_40, "exp(noise_Intercept + noise_dose) - exp(noise_Intercept) > 0", alpha = 0.025)
hyp_muscimol_noise
plot(hyp_muscimol_noise)
```

## bi muscimol lognoise_dose
```{r echo=T, comment=NA}

hyp_muscimol_noise_dose <- hypothesis(bi_ppc_muscimol_cdf_40, "noise_dose > 0", alpha = 0.025)
hyp_muscimol_noise_dose
plot(hyp_muscimol_noise_dose)
```


## test for bi muscimol delta rational
```{r echo=T, comment=NA}

hyp_muscimol_omega_rational <- hypothesis(bi_ppc_muscimol_cdf_40, "inv_logit(omega1_Intercept + omega1_dose) - inv_logit(omega1_Intercept) < 0", alpha = 0.025)
hyp_muscimol_omega_rational
plot(hyp_muscimol_omega_rational)
```

## bi muscimol omega1_dose
```{r echo=T, comment=NA}

hyp_muscimol_omega1_dose <- hypothesis(bi_ppc_muscimol_cdf_40, "omega1_dose < 0", alpha = 0.025)
hyp_muscimol_omega1_dose
plot(hyp_muscimol_omega1_dose)
```


## test for bi muscimol delta lottery
```{r echo=T, comment=NA}

hyp_muscimol_omega_lottery <- hypothesis(bi_ppc_muscimol_cdf_40, "(1- inv_logit(omega1_Intercept + omega1_dose))*inv_logit(omega2_Intercept + omega2_dose) - (1- inv_logit(omega1_Intercept))*inv_logit(omega2_Intercept) < 0", alpha = 0.025)
hyp_muscimol_omega_lottery
plot(hyp_muscimol_omega_lottery)
```


## bi muscimol omega2_dose
```{r echo=T, comment=NA}

hyp_muscimol_omega2_dose <- hypothesis(bi_ppc_muscimol_cdf_40, "omega2_dose < 0", alpha = 0.025)
hyp_muscimol_omega2_dose
plot(hyp_muscimol_omega2_dose)
```

## test for bi muscimol delta surebet
```{r echo=T, comment=NA}

hyp_muscimol_omega_surebet <- hypothesis(bi_ppc_muscimol_cdf_40, "(1- inv_logit(omega1_Intercept + omega1_dose))*(1-inv_logit(omega2_Intercept + omega2_dose)) - (1- inv_logit(omega1_Intercept))*(1-inv_logit(omega2_Intercept)) > 0", alpha = 0.025)
hyp_muscimol_omega_surebet
plot(hyp_muscimol_omega_surebet)
```

# unilateral fof muscimol
## test for uni muscimol delta raw rho
```{r echo=T, comment=NA}

hyp_muscimol_rho <- hypothesis(uni_ppc_muscimol_cdf_40, "exp(logrho_Intercept + logrho_dose) - exp(logrho_Intercept) < 0", alpha = 0.025)
hyp_muscimol_rho
plot(hyp_muscimol_rho)
```

## uni muscimol logrho_dose
```{r echo=T, comment=NA}

hyp_muscimol_rho_dose <- hypothesis(uni_ppc_muscimol_cdf_40, "logrho_dose < 0", alpha = 0.025)
hyp_muscimol_rho_dose
plot(hyp_muscimol_rho_dose)
```


## test for uni muscimol delta raw noise
```{r echo=T, comment=NA}

hyp_muscimol_noise <- hypothesis(uni_ppc_muscimol_cdf_40, "exp(noise_Intercept + noise_dose) - exp(noise_Intercept) > 0", alpha = 0.025)
hyp_muscimol_noise
plot(hyp_muscimol_noise)
```

## uni muscimol lognoise_dose
```{r echo=T, comment=NA}

hyp_muscimol_noise_dose <- hypothesis(uni_ppc_muscimol_cdf_40, "noise_dose > 0", alpha = 0.025)
hyp_muscimol_noise_dose
plot(hyp_muscimol_noise_dose)
```


## test for uni muscimol delta rational
```{r echo=T, comment=NA}

hyp_muscimol_omega_rational <- hypothesis(uni_ppc_muscimol_cdf_40, "inv_logit(omega1_Intercept + omega1_dose) - inv_logit(omega1_Intercept) < 0", alpha = 0.025)
hyp_muscimol_omega_rational
plot(hyp_muscimol_omega_rational)
```

## uni muscimol omega1_dose
```{r echo=T, comment=NA}

hyp_muscimol_omega1_dose <- hypothesis(uni_ppc_muscimol_cdf_40, "omega1_dose < 0", alpha = 0.025)
hyp_muscimol_omega1_dose
plot(hyp_muscimol_omega1_dose)
```


## test for uni muscimol delta lottery
```{r echo=T, comment=NA}

hyp_muscimol_omega_lottery <- hypothesis(uni_ppc_muscimol_cdf_40, "(1- inv_logit(omega1_Intercept + omega1_dose))*inv_logit(omega2_Intercept + omega2_dose) - (1- inv_logit(omega1_Intercept))*inv_logit(omega2_Intercept) < 0", alpha = 0.025)
hyp_muscimol_omega_lottery
plot(hyp_muscimol_omega_lottery)
```


## uni muscimol omega2_dose
```{r echo=T, comment=NA}

hyp_muscimol_omega2_dose <- hypothesis(uni_ppc_muscimol_cdf_40, "omega2_dose < 0", alpha = 0.025)
hyp_muscimol_omega2_dose
plot(hyp_muscimol_omega2_dose)
```

## test for uni muscimol delta surebet
```{r echo=T, comment=NA}

hyp_muscimol_omega_surebet <- hypothesis(uni_ppc_muscimol_cdf_40, "(1- inv_logit(omega1_Intercept + omega1_dose))*(1-inv_logit(omega2_Intercept + omega2_dose)) - (1- inv_logit(omega1_Intercept))*(1-inv_logit(omega2_Intercept)) > 0", alpha = 0.025)
hyp_muscimol_omega_surebet
plot(hyp_muscimol_omega_surebet)
```

# chech the whole sessions for the PPC data
```{r echo=T, comment=NA}

hyp_muscimol_rho <- hypothesis(bi_ppc_muscimol_cdf, "exp(logrho_Intercept + logrho_dose) - exp(logrho_Intercept) < 0", alpha = 0.025)
hyp_muscimol_rho
plot(hyp_muscimol_rho)
```

## bi muscimol logrho_dose
```{r echo=T, comment=NA}

hyp_muscimol_rho_dose <- hypothesis(bi_ppc_muscimol_cdf, "logrho_dose < 0", alpha = 0.025)
hyp_muscimol_rho_dose
plot(hyp_muscimol_rho_dose)
```


## test for bi muscimol delta raw noise
```{r echo=T, comment=NA}

hyp_muscimol_noise <- hypothesis(bi_ppc_muscimol_cdf, "exp(noise_Intercept + noise_dose) - exp(noise_Intercept) > 0", alpha = 0.025)
hyp_muscimol_noise
plot(hyp_muscimol_noise)
```

## bi muscimol lognoise_dose
```{r echo=T, comment=NA}

hyp_muscimol_noise_dose <- hypothesis(bi_ppc_muscimol_cdf, "noise_dose > 0", alpha = 0.025)
hyp_muscimol_noise_dose
plot(hyp_muscimol_noise_dose)
```


## test for bi muscimol delta rational
```{r echo=T, comment=NA}

hyp_muscimol_omega_rational <- hypothesis(bi_ppc_muscimol_cdf, "inv_logit(omega1_Intercept + omega1_dose) - inv_logit(omega1_Intercept) < 0", alpha = 0.025)
hyp_muscimol_omega_rational
plot(hyp_muscimol_omega_rational)
```

## bi muscimol omega1_dose
```{r echo=T, comment=NA}

hyp_muscimol_omega1_dose <- hypothesis(bi_ppc_muscimol_cdf, "omega1_dose < 0", alpha = 0.025)
hyp_muscimol_omega1_dose
plot(hyp_muscimol_omega1_dose)
```


## test for bi muscimol delta lottery
```{r echo=T, comment=NA}

hyp_muscimol_omega_lottery <- hypothesis(bi_ppc_muscimol_cdf, "(1- inv_logit(omega1_Intercept + omega1_dose))*inv_logit(omega2_Intercept + omega2_dose) - (1- inv_logit(omega1_Intercept))*inv_logit(omega2_Intercept) < 0", alpha = 0.025)
hyp_muscimol_omega_lottery
plot(hyp_muscimol_omega_lottery)
```


## bi muscimol omega2_dose
```{r echo=T, comment=NA}

hyp_muscimol_omega2_dose <- hypothesis(bi_ppc_muscimol_cdf, "omega2_dose < 0", alpha = 0.025)
hyp_muscimol_omega2_dose
plot(hyp_muscimol_omega2_dose)
```

## test for bi muscimol delta surebet
```{r echo=T, comment=NA}

hyp_muscimol_omega_surebet <- hypothesis(bi_ppc_muscimol_cdf, "(1- inv_logit(omega1_Intercept + omega1_dose))*(1-inv_logit(omega2_Intercept + omega2_dose)) - (1- inv_logit(omega1_Intercept))*(1-inv_logit(omega2_Intercept)) > 0", alpha = 0.025)
hyp_muscimol_omega_surebet
plot(hyp_muscimol_omega_surebet)
```

# unilateral fof muscimol
## test for uni muscimol delta raw rho
```{r echo=T, comment=NA}

hyp_muscimol_rho <- hypothesis(uni_ppc_muscimol_cdf, "exp(logrho_Intercept + logrho_dose) - exp(logrho_Intercept) < 0", alpha = 0.025)
hyp_muscimol_rho
plot(hyp_muscimol_rho)
```

## uni muscimol logrho_dose
```{r echo=T, comment=NA}

hyp_muscimol_rho_dose <- hypothesis(uni_ppc_muscimol_cdf, "logrho_dose < 0", alpha = 0.025)
hyp_muscimol_rho_dose
plot(hyp_muscimol_rho_dose)
```


## test for uni muscimol delta raw noise
```{r echo=T, comment=NA}

hyp_muscimol_noise <- hypothesis(uni_ppc_muscimol_cdf, "exp(noise_Intercept + noise_dose) - exp(noise_Intercept) > 0", alpha = 0.025)
hyp_muscimol_noise
plot(hyp_muscimol_noise)
```

## uni muscimol lognoise_dose
```{r echo=T, comment=NA}

hyp_muscimol_noise_dose <- hypothesis(uni_ppc_muscimol_cdf, "noise_dose > 0", alpha = 0.025)
hyp_muscimol_noise_dose
plot(hyp_muscimol_noise_dose)
```


## test for uni muscimol delta rational
```{r echo=T, comment=NA}

hyp_muscimol_omega_rational <- hypothesis(uni_ppc_muscimol_cdf, "inv_logit(omega1_Intercept + omega1_dose) - inv_logit(omega1_Intercept) < 0", alpha = 0.025)
hyp_muscimol_omega_rational
plot(hyp_muscimol_omega_rational)
```

## uni muscimol omega1_dose
```{r echo=T, comment=NA}

hyp_muscimol_omega1_dose <- hypothesis(uni_ppc_muscimol_cdf, "omega1_dose < 0", alpha = 0.025)
hyp_muscimol_omega1_dose
plot(hyp_muscimol_omega1_dose)
```


## test for uni muscimol delta lottery
```{r echo=T, comment=NA}

hyp_muscimol_omega_lottery <- hypothesis(uni_ppc_muscimol_cdf, "(1- inv_logit(omega1_Intercept + omega1_dose))*inv_logit(omega2_Intercept + omega2_dose) - (1- inv_logit(omega1_Intercept))*inv_logit(omega2_Intercept) < 0", alpha = 0.025)
hyp_muscimol_omega_lottery
plot(hyp_muscimol_omega_lottery)
```


## uni muscimol omega2_dose
```{r echo=T, comment=NA}

hyp_muscimol_omega2_dose <- hypothesis(uni_ppc_muscimol_cdf, "omega2_dose < 0", alpha = 0.025)
hyp_muscimol_omega2_dose
plot(hyp_muscimol_omega2_dose)
```

## test for uni muscimol delta surebet
```{r echo=T, comment=NA}

hyp_muscimol_omega_surebet <- hypothesis(uni_ppc_muscimol_cdf, "(1- inv_logit(omega1_Intercept + omega1_dose))*(1-inv_logit(omega2_Intercept + omega2_dose)) - (1- inv_logit(omega1_Intercept))*(1-inv_logit(omega2_Intercept)) > 0", alpha = 0.025)
hyp_muscimol_omega_surebet
plot(hyp_muscimol_omega_surebet)
```










